Real Time Fluid Simulation \\ \smaller using Smoothed-Particle Hydrodynamics and OpenGL

### 2014-12-07 paper/paper.tex
Velocity Verlet Implemented, but still has bugs + Added velocity verlet scheme to report

\usepackage[hyperref=true,style=authoryear,backend=biber]{biblatex}
\usepackage{filecontents}
\usepackage{setspace}
\usepackage{fancyhdr}

@@

\section{Mathematical Background}

>>>>

\usepackage[hyperref=true,style=authoryear,backend=biber]{biblatex}
\usepackage{filecontents}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage[ruled,vlined]{algorithm2e}

@@

\section{Mathematical Background}
%
\begin{align}
	a_i^n = \frac{F_i^n}{m_i} = \dots
	\label{math:acceleration}
\end{align}

\section{The Algorithm}
%
In the following, we denote the position for the particle $i$ at time $t$ as $x_i^t$, its velocity as $v_i^t$ and its acceleration as $a_i^t$.
We omit the vector notation ($\boldsymbol{x},\boldsymbol{v},\boldsymbol{a}$) for these quantities, since the following equations are valid for the vectors as well as for each component individually.
\par\medskip
%
As suggested in \cite{generalizedwallboundary}, we use the \emph{Velocity-Verlet} time stepping scheme as follows:
%
\begin{algorithm}
	\caption{Single Timestep with Velocity Verlet Algorithm}
	\KwData{$x_i^t$, $v_i^{t - \frac{\Delta t}{2}}$, $a_i^t$, $\Delta t$}
	\KwResult{$x_i^{t + \Delta t}$, $v_i^{t + \frac{\Delta t}{2}}$, $a_i^{t + \Delta t}$}	
	$v_i^{t+\frac{\Delta t}{2}} = v_i^{t - \frac{\Delta t}{2}} + \Delta t a_i^t$ \;
	$x_i^{t+\Delta t} = x_i^t + \Delta t v_i^{t+\frac{\Delta t}{2}}$ \;	
	$a_i^{t + \Delta t} = a_i^{t + \Delta t} (x_i^{t + \Delta t}, m_i)$ from equation \ref{math:acceleration} \;
\end{algorithm}
